Fairness in Machine Learning SS21

### 2021-05-13 references/vanilla_presentation .Rmd
yellow

---
title: "Fairness in Machine Learning SS21"
subtitle: "Beyond Static Fairness"
date: "03/05/2021"
author: "Daniel Saggau"
output:
  beamer_presentation:
    theme: Madrid
    colortheme: spruce
---

>>>>

---
title: "Fairness in Machine Learning SS21"
subtitle: "Beyond Static Fairness"
date: "03/05/2021"
author: "Daniel Saggau"
output:
  beamer_presentation:
    theme: Madrid
    colortheme: crane
---
